\documentclass[10pt, oneside]{article}




\begin{document}

\title{The \texttt{thesisfrontmatter} package
\footnote{This file has version number v1.0, last revised on 11/21/02}}
\author{Emmett J. Ientilucci \\
Chester F. Carlson Center for Imaging Science \\
Rochester Institute of Technology \\
emmett@cis.rit.edu \\}
\date{November 21, 2002}
\maketitle

\begin{abstract}
The purpose of this package is to automatically generate all the front matter found in a
Rochester Institute of Technology (RIT), Center for Imaging Science (CIS) thesis or
dissertation. This front matter is created for both an M.S. or Ph.D. proposal, thesis, or
dissertation.
\end{abstract}

\section{Introduction}
The introductory pages found in every proposal, thesis, or dissertation are crucial to
the completeness of the report, not to mention the importance of graduation.  The
introductory pages usually include a declaration page, approval page, and copyright page.
Additionally, one nominally includes one or all of the following: an abstract page, an
acknowledgements page, and/or a dedication page. The \verb"thesisfrontmatter" package
creates any one of these pages by first defining some variables within the
\textit{document class} and then by calling a simple command to create the desired page
of interest.

\section{Usage}
The package can be used by entering the command \\

\verb"\usepackage[option]{thesisfrontmatter}" \\

\noindent in the preamble of the document.  The option field is either \verb"ms" or
\verb"phd" where \verb"ms" creates the formatted front matter for a masters thesis or
proposal and \verb"phd" creates the formatted front matter for a doctorate of philosophy
dissertation or proposal. The package or style file (\verb".sty"), can be placed in the
current working directory or off your local \texttt{texmf} directory structure
(\textit{e.g.} \verb"C:\localtexmf\tex\latex\").

In order to create the necessary pages with titles, authors, committee members, etc. in
it, the following fields should be defined, as needed, within the \textit{document
class}.

\begin{verbatim}
\degreetitle{}
\degreeauthor{}
\prevdegreeA{}
\prevdegreeB{}
\prevdegreeC{}
\degreedate{}
\advisor{}
\memberA{}
\memberB{}
\memberC{}
\memberD{}
\end{verbatim}

Once the appropriate fields have been defined, the desired front matter page can be
created by using one (or all) of the following commands.

\begin{verbatim}
\makeproposaldeclaration
\makeproposalapproval
\makedeclaration
\makeapproval
\makecopyright
\end{verbatim}

One only needs to define the fields that are applicable for the desired front matter
page. These dependencies can be seen below. \\

\fbox{$\backslash$\texttt{makeproposaldeclaration}} requires the definition of
\verb"\degreetitle{}", \verb"\degreeauthor{}", and \verb"\degreedate{}". \\

\fbox{$\backslash$\texttt{makeproposalapproval}} requires the definition
of \verb"\degreeauthor{}" and \verb"\advisor{}". \\

\fbox{$\backslash$\texttt{makedeclaration}} requires the definition of
\verb"\degreetitle{}", \verb"\degreeauthor{}", \verb"\prevdegreeA{}",
etc., and \verb"\degreedate{}". \\

\fbox{$\backslash$\texttt{makeapproval}} requires the definition of
\verb"\degreeauthor{}", \verb"\advisor{}", \verb"\memberA{}",
\verb"\memberB{}", etc. \\

\fbox{$\backslash$\texttt{makecopyright}} requires the definition
of \verb"\degreetitle{}" and \verb"\degreeauthor{}". \\




\subsection{Other \texttt{thesisfrontmatter} Environments}
In addition to the pages described above, there are three formatted environments that
have been created as well.  These are for the creation of the abstract, acknowledgements,
and dedication pages.  They can be used by simply typing the following within the
 \textit{document class}\\

\noindent
\verb"\begin{"\textit{environment}\verb"}" \\
\textit{text} \\
\verb"\end{"\textit{environment}\verb"}" \\

where environment is either \verb"abstract", \verb"acknowledgements", or
\texttt{dedication}. The abstract environment creates a new page with formatted title
information on it.  Therefore, it requires the definition of the fields
\verb"\degreetitle" and \verb"\degreeauthor".

The acknowledgements environment also creates a new page and simply places the word
``acknowledgements" at the top of the page.  Finally, the dedication environment creates a
new page that has centered and italicized text on it.




\subsection{Final Page Formatting Comments}
In addition to creating all the above mentioned pages, the \texttt{thesisfrontmatter}
package also changes the overall page layout of the document (based on the \textit{book}
class). That is, the page height and width have been changed to 20 cm and 14.5 cm,
respectively. Feel free to email me if you have any questions.  Happy \TeX ing!!




\section{Example}
Below is an example of how one might use the \texttt{thesisfrontmatter} package to create
 front matter for the declaration, approval, copyright, abstract,
acknowledgements, and dedication pages for a Ph.D. dissertation.
\begin{verbatim}
\documentclass[11pt, oneside]{book}

\usepackage[phd]{thesisfrontmatter}

\begin{document}
\degreetitle{A New Approach to Bivariant K-theory}
\degreeauthor{Dorin Dumitrascu}
\degreedate{May 28, 2000}
\prevdegreeA{B.S. Penn State University, 1994}
\prevdegreeB{M.S. Stony Brook University, 1998}
\advisor{Dr. Arkady Tempelman}
\memberA{Dr. Nigel Higson}
\memberB{Dr. Wen-Ching Winnie Li}
\memberC{Dr. Diane Henderson}

\makedeclaration
\makeapproval
\makecopyright

\begin{abstract}
This is the abstract text
\end{abstract}

\begin{acknowledgements}
This is the acknowledgements text
\end{acknowledgements}

\begin{dedication}
This is the dedication text
\end{dedication}

\include{chapter1_introduction}
\include{chapter2_background}

\end{document}
\end{verbatim}


\end{document}
